A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-02-05 README.Rmd
added abstract to README

>>>>

European Bronze Age archaeology traditionally focusses on two major dimensions to categorise burials -- although there is an immense variability of attendant phenomena within this spectrum -- flat graves versus burial mounds and cremation versus inhumation. These traits are an indispensable ingredient for common archaeological narratives of sociocultural interaction and cultural evolution. This paper presents a quantitative reconstruction of the general trends in the distribution of Bronze Age burial traditions based on bulk radiocarbon data and employs the resulting time series for the estimation of macro-regional cultural distance. Despite the relatively small amount of input data the trend reconstruction fits to established archaeological observations for prehistoric Europe. The comparison of cultural and spatial distance leads to the remarkable result of no significant permanent correlation, which indicates that the spread of the relevant aspects of burial traditions can not be explained with simple diffusion models. Instead a more complex process of cultural transmission has to be considered.

### Keywords:

Bronze Age, Burial Traditions, Cultural Evolution, Cultural Transmission
